---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# detourr

Animations for {tourr} using htmlwidgets for performance and portability.

# Installation

Install this package by running the following in R:

```{r, eval=FALSE}
remotes::install_github("casperhart/detourr")
``` 

# Examples

```{r, eval=FALSE}
# 2D scatter
library(tourr)
library(detourr)
animate_tour(
  olive,
  display = display_scatter(tour_aes(colour = region)),
)
```

```{r, eval=FALSE}
# 3D scatter
animate_tour(
  flea,
  grand_tour(3),
  display_scatter(tour_aes(colour = species))
)
```

# Development

## Getting Started

This project uses TypeScript code which needs to be compiled and bundled for
the package to work. To do this, you will need `node.js`, and `yarn`
installed.

After cloning this repository, you can install the node.js dependencies via:

```{bash, eval=FALSE}
yarn install
```

Compile and bundle the TypeScript code and install the R package from source by
running:

```{bash, eval=FALSE}
yarn run build
```

The TypeScript code which powers the HTMLWidgets can also be run as a
standalone app using `webpack-dev-server` as follows:

```{bash, eval=FALSE}
yarn run start-dev
```

This will start the webpack dev server, which will automatically recompile and
reload the TypeScript code as changes are made.
The sample data and HTML used by the dev server can be found in `./dev`, and
are loaded in to memory based on the configuration in `webpack/dev.config.ts`

If you wish to make changes to the HTML files in `dev/`, or debug the
`yarn run start-dev` command, you can instead run `yarn run build-dev`.
This will load the files in `dev/` in to a folder called `dev_build/` rather
than in to memory, which can make debugging easier.

## Adding a new widget

The following is a rough checklist for creating a new widget / visualisation
for the {detourr} package. This uses `display_scatter_3d` as an example.

1. `srcts/display_scatter_3d`: The main logic for the `display_scatter_3d`
   widget. Note that the main exported class from `index.ts` contains a
   `renderValue` and `resize` method (inherited from `DisplayScatter`).
   This exported class and methods are used by the HTMLWidgets Javascript
   binding.
2. `inst/htmlwidgets/display_scatter_3d.js`: Javascript binding for HTMLWidgets.
3. `inst/htmlwidgets/display_scatter_3d.yaml`: widget dependencies. Note that
   the dependencies are all stored under `inst/htmlwidgets/lib`, and should
   not be modified manually. These files are automatically bundled by webpack
   based on the code in `srcts/` and the configuration in
   `webpack/package.config.json`.
4. `R/display_scatter.r`: R binding for the widget. Returns an `init` function
   used by `animate_tour.r` to define the widget to create. Note that
   `display_scatter.r` services both the `display_scatter_3d` and
   `display_scatter_2d` widgets. See the
   [HTMLWidgets Documentation](https://www.htmlwidgets.org/develop_intro.html)
   for more information on the Javascript binding, R binding, and widget
   dependencies.
5. `dev/display_scatter_3d`: sample data and HTML file used for development.
   The presence of these files allows the widget to be run standalone, without
   the need to build and run the R package every time a change is made. These
   files are loaded in to memory when the webpack dev server is started, based
   on the configuration in `webpack/dev.config.ts`.
6. `webpack/dev.config.ts`: webpack development config. Each widget has an
   entry in this file under `entry`, pointing to the `index.ts` file for that
   widget, and a pattern under `CopyPlugin` so that it knows to find dev assets
   (`index.html` and `sample_data.json`) under `dev/display_scatter_3d`. This
   config file is used when running `yarn run start-dev` and
   `yarn run build-dev`.
7. `webpack/package.config.ts`: webpack configuration used when building the
   package. Each widget has a value under `entry` in this file.
