---
output: 
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# d3tourr

Animations for {tourr} using htmlwidgets for performance and portability.

# Installation

Install this package by running `remotes::install_github("casperhart/d3tourr")` in R.

# Development

This project uses TypeScript code which needs to be compiled and bundled for the package to work. To do this, you will need `node.js`, and `yarn` installed.

After cloning this repository, you can install the node.js dependencies via:

```{bash, eval=FALSE}
yarn install
```

Compile and bundle the TypeScript code and install the R package from source by running:

```{bash, eval=FALSE}
yarn run build
```

The TypeScript code which powers the HTMLWidgets can also be run as a standalone app using `webpack-dev-server` as follows:

```{bash, eval=FALSE}
yarn run start-dev
```

This will start the webpack dev server, which will automatically recompile and reload the TypeScript code as changes are made.
The sample data and HTML used for development can be found in `./dev`

# Examples

```{r, eval=FALSE}
library(d3tourr)
animate_tour(
  tourr::flea,
  -species,
  display = display_scatter(tour_aes(colour = species)),
  render_opts = list(max_bases = 10)
)
```
